---
title: "STAT 302 SPR2020 Lecture 15"
author: "Sheridan Grant"
date: "May 18, 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Preliminaries

Libraries:
```{r}
library(tidyverse)
```

Read SAT data, Tidy way
```{r}
sat <- read_csv('../data/sat.csv')
sat %>% head()  # that weird i-umlaut thing is gone!
sat$sex <- ifelse(sat$sex == 1, 'male', 'female')
n <- dim(sat)[1]
head(sat)
```

COVID-19
```{r}
covid <- read_csv("../data/coronavirus.csv",
                  col_types = cols(Admin2 = col_character(),
                                   Date = col_date('%m/%d/%Y')))
head(covid)  # first colname correct already, date already good to go
```

## ggplot, cont'd

### Multivariate plots

Last class, we saw how to use the "color" aesthetic to display more than two variables on a plot.

Chat Q1: what goes wrong here? How can I fix it?
```{r}
ggplot(sat) +
  geom_point(mapping = aes(x = HSGPA, y = FYGPA), color = 'blue', size = 1)
```

We can use transformations of variables, just as we commonly did with dplyr
```{r}
ggplot(sat) +
  geom_point(aes(HSGPA, FYGPA, color = SATSum < 100))

ggplot(sat) +
  geom_point(aes(HSGPA, FYGPA, color = SATSum < 100), show.legend = F)
```

Can convey information with more than just color
```{r}
ggplot(sat) +
  geom_point(aes(HSGPA, FYGPA, alpha = SATSum/200))
```

```{r}
ggplot(sat) +
  geom_point(aes(HSGPA, FYGPA, size = SATSum))
```

What is misleading about the above plot?

```{r}
ggplot(sat) +
  geom_jitter(aes(HSGPA, FYGPA, alpha = SATSum/200))

plot(jitter(sat$HSGPA,5), jitter(sat$FYGPA,5))
plot(sat$HSGPA, sat$FYGPA)
```

#### Facets

Dunno why these are called this, but whatever. Pretty clear what they do:

```{r}
ggplot(sat, aes(x = HSGPA, y = FYGPA)) +
  geom_smooth() + geom_point() +
  facet_wrap(~sex)
```

These curves are known colloquially as "smoothers." They are designed to show trends in observed data rather than predict on new data. I don't ever use them.

```{r}
ggplot(sat, aes(x = HSGPA, y = FYGPA)) +
  geom_smooth() + geom_point() +
  facet_grid(sex ~ SATSum)
```

Whoops... best stick to factors!

```{r}
ggplot(sat, aes(x = HSGPA, y = FYGPA)) +
  geom_smooth() + geom_point() +
  facet_grid(sex ~ SATSum > 100)
```

Check out that bottom left panel, right-hand side! These smoothing curves are *terrible* predictors.

### Advanced Aesthetics

```{r}
ggplot(sat, aes(x = HSGPA, y = FYGPA)) +
  geom_point() +
  geom_smooth(aes(group = SATSum > 120))
```

A different approach that makes labeling easy:
```{r}
ggplot(sat, aes(x = HSGPA, y = FYGPA)) +
  geom_point() +
  geom_smooth(aes(color = SATSum > 120))
```

Some geoms have extra aesthetics that do cool things like this. Of course, this can be done with a bit more typing without knowing about "group":
```{r}
ggplot(sat) +
  geom_point(mapping = aes(x = HSGPA, y = FYGPA)) +
  geom_smooth(data = sat %>% filter(SATSum > 120), aes(x = HSGPA, y = FYGPA)) +
  geom_smooth(data = sat %>% filter(SATSum <= 120), aes(x = HSGPA, y = FYGPA))
```

In fact, you can specify the data and aesthetic mapping for each layer totally separately:

```{r}
ggplot() +
  geom_point(data = sat, aes(x = HSGPA, y = FYGPA)) +
  geom_smooth(data = sat %>% filter(SATSum > 120), aes(x = HSGPA, y = FYGPA)) +
  geom_smooth(data = sat %>% filter(SATSum <= 120), aes(x = HSGPA, y = FYGPA))
```

But woe unto you if you use this without thinking:
```{r}
ggplot(sat) +
  geom_point(aes(x = sex, y = SATSum)) +
  geom_smooth(aes(x = HSGPA, y = FYGPA))
```

### Plotting Statistics

A *statistic* is a function of the data, like the sample mean or empirical skewness.

```{r}
sat$satGroup <- (sat$SATSum < 55) + (sat$SATSum < 70) + (sat$SATSum < 85) + (sat$SATSum < 100) + (sat$SATSum < 115) + (sat$SATSum < 130) + (sat$SATSum < 145) + (sat$SATSum <= 160)

sat$satGroup <- factor(sat$satGroup, levels = 1:8)
ggplot(sat) +
  geom_bar(aes(x = satGroup))

sat %>% count(satGroup)
```

Of course, what we're really looking for is
```{r}
ggplot(sat) + geom_histogram(aes(x = SATSum))
```

...these kids must've been cheating like mad!

### Advanced Multivariate Plots

Bar chart from earlier
```{r}
ggplot(sat) + geom_bar(aes(x = satGroup, color = HSGPA > 3))
```

Hideous. We need "fill":
```{r}
ggplot(sat) + geom_bar(aes(x = satGroup, fill = HSGPA > 3))
```

or position = 'dodge':
```{r}
ggplot(sat) + geom_bar(aes(x = satGroup, fill = HSGPA > 3), position = 'dodge')
```

Or just use faceting. Then you don't get the misleading double-wide bars in groups 7 and 8.
```{r}
ggplot(sat) +
  geom_bar(aes(x = HSGPA > 3)) +
  facet_wrap(~ satGroup, nrow = 2)
```

## Selected Other Data Science Skills

### User Input

When writing software, especially to be used by folks who don't code, it can be useful to ask for user input. Like:
```{r}
cat('Name is:', readline('What name?'))
```

Handy! Or:
```{r}
mySquare <- function() {
  x <- readline('input number you wanna square')
  x <- as.numeric(x)
  x^2
}
mySquare()
```

What if the user wants to input multiple numbers?
```{r}
mySquare <- function() {
  x <- readline('input numbers you wanna square, separated by commas: ')
  x <- as.numeric(unlist(strsplit(x, ',')))
  x^2
}
mySquare()
```

...unlist? strsplit?
```{r}
x <- c('1, 2, 3')
strsplit(x, ',')
unlist(strsplit(x, ','))
unlist(list(1,2,3))
```

### stringr

If your final project includes text data, you may need to manipulate it programmatically. This can be a hassle, but Tidyverse's stringr is here to help.

Concatenate (character) strings like "+" in Python:
```{r}
str_c('Sheridan', 'Lloyd', 'Grant')
str_c('Sheridan', 'Lloyd', 'Grant', sep = ' ')
```

Vectorized:
```{r}
x <- c('Sheridan Grant', 'General Kenobi')
str_c('Hello there, ', x, '!')[2]  # I know I butchered the actual quote don't @ me
str_c(x, rev(x), 1:4)  # wild
```

Collapsing:
```{r}
str_c(rep(x, 2), collapse = ' admires ')  # a classic bromance
```

Trimming:
```{r}
str_trim('   Have you heard the story?   ', side = 'left')
str_trim('   Have you heard the story?   ', side = 'right')
str_trim('   Have you heard the story?   ', side = 'both')
str_squish('   Have    you       heard      the      story?   ')
```

Subsetting:
```{r}
str_sub(x, 3)
str_sub(x, -3)
str_sub(x, 3, 12)
str_sub(x, 3, -3)
```


### Regular Expressions

You may have seen '\n' in my solutions, particularly when I use cat:
```{r}
cat('Name is:', readline('Name? '), '\n',
    'Fav number is:', readline('Fav number? '))
```

This is interpreted as a newline, even though I didn't type a newline! '\n' is a regular expression, or regex.

Basic pattern matching:
```{r}
x <- c(x, 'Hello there.', 'What about the droid attack on the wookies?')
str_view(x, 'er')
str_view_all(x, '. .')  #'.' is a regex for "any single character"
str_view(x, '\.')  # This doesn't work because backlash is itself a character
str_view(x, '\\.')  # 'Double escape'
str_view(x, '^G')  # ^ anchors to beginning
str_view(x, 't$')  # $ anchors to end
```

How to actually use it in code?
```{r}
str_detect(x, 'er')
str_detect(x, '\\.')
```

