---
title: "STAT 302 SPR2020 Homework 9 Graded Solution"
author: "Sheridan Grant"
date: "6/1/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
Collaborators: moi, yo, myself

Required libraries:
```{r, warning=F, message=F}
library(tidyverse)
library(data.table)
```

Helper functions:
```{r}
expit <- function(x) exp(x)/(exp(x) + 1)
acc <- function(y, yhat) mean(y == yhat)
```


## Question 1

Check students' code for this one, as computers will behave differently.

### Part a

readr
```{r}
t0 <- Sys.time()
covid_tidy <- read_csv("../data/coronavirus.csv",
                       col_types = cols(Admin2 = col_character(),
                                        Date = col_date('%m/%d/%Y')))
t1 <- Sys.time()
cat('readr read_csv time for covid:', t1-t0, '\n')
```

data.table
```{r}
t2 <- Sys.time()
covid_dt <- fread("../data/coronavirus.csv")
covid_dt$Date <- as.Date(covid_dt$Date, format = '%m/%d/%Y')
t3 <- Sys.time()
cat('data.table fread time for covid:', t3-t2, '\n')
```

data.table 3-4x faster!

### Part b

dplyr
```{r}
t4 <- Sys.time()
covid_tidy %>% arrange(Date) -> covid_tidy
t5 <- Sys.time()
cat('dplyr arrange time for covid:', t5-t4, '\n')
```

data.table
```{r}
t6 <- Sys.time()
covid_dt %>% setorder('Date')
t7 <- Sys.time()
cat('data.table setorder time for covid:', t7-t6, '\n')
```

data.table 3-4x faster!

### Part c

dplyr
```{r}
t8 <- Sys.time()
covid_tidy %>%
  select(Date, Country_Region, Province_State, Admin2, Case_Type, Cases) %>%
  spread(Case_Type, Cases) -> covid_tidy
head(covid_tidy)
dim(covid_tidy)
t9 <- Sys.time()
cat('dplyr spread time for covid:', t9-t8, '\n')
```

data.table
```{r}
t10 <- Sys.time()
covid_dt %>% dcast(Country_Region+Province_State+Admin2+Date~Case_Type,
                   value.var = "Cases") -> covid_dt
head(covid_dt)
dim(covid_dt)
t11 <- Sys.time()
cat('data.table dcast time for covid:', t11-t10, '\n')
```

data.table 3x faster!

## Question 2

```{r}
quora <- read_csv('../data/quoraSmall.csv')
n <- nrow(quora)
```

### Part a

```{r}
qs <- c('who', 'what', 'when', 'where', 'why', 'how')

percs <- sapply(qs, function(q) quora %>% filter(str_detect(question_text, str_c('(?i)', q))) %>% nrow()/n)

otherPerc <- 1 - sum(percs)
qTypes <- c(percs, otherPerc)
qTypes
```

### Part b

```{r}
quora %>% 
  filter(str_detect(question_text, '^.*\\.{1} {1}')) %>%
  nrow()/n

quora %>% 
  filter(str_detect(question_text, '^.*\\.{1} {1}')) %>%
  summarize(trollPerc = mean(target))

mean(quora$target)
```

Somewhat more likely. Perhaps a statement in a question can be meant to bias readers?

### Part c

```{r}
quora %>% 
  mutate(vac = str_detect(question_text, '(?i)vaccin'),
         qq = str_detect(question_text, '\\?{2,}'),
         per = str_detect(question_text, '^.*\\.{1} {1}')) ->
  quora

trollMod <- glm(target ~ vac + qq + per, data = quora[1:90000,], family = 'binomial')
summary(trollMod)

f <- function(x) x > expit(coef(trollMod)[1])
preds <- predict(trollMod, quora[90001:n,], type = 'response')
acc(f(preds), quora[90001:n,'target'])
```

We get 94% accuracy by just using a prediction of "not troll" every time (only 6% troll questions)--without using covariates or the questions themselves at all! Our prediction rule doesn't do better in terms of accuracy because even though we may be identifying Troll questions at > 6% accuracy, we aren't beating 94%! When the two outcome classes are this imbalanced, accuracy is usually unhelpful.