---
title: "STAT 302 SPR2020 Lecture 17"
author: "Sheridan Grant"
date: "May 27, 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Preliminaries

Libraries:
```{r}
library(tidyverse)
```

COVID-19
```{r}
covid <- read_csv("../data/coronavirus.csv",
                  col_types = cols(Admin2 = col_character(),
                                   Date = col_date('%m/%d/%Y')))
head(covid)  # first colname correct already, date already good to go
```


## Huge Data

Brief demonstration of data.table, as some of you have big data for your final project:
```{r}
library(data.table)
slowQuora <- read_csv('../data/quora.csv')
fastQuora <- fread('../data/quora.csv')  # woah
slowQuora %>% arrange(qid) -> slowQuora
fastQuora %>% setorder('qid')  # faster AND uses less memory by not copying
```

## stringr

If your final project includes text data like the Quora data, you may need to manipulate it programmatically. This can be a hassle, but Tidyverse's stringr is here to help.

Concatenate (character) strings like "+" in Python:
```{r}
str_c('Sheridan', 'Lloyd', 'Grant')
str_c('Sheridan', 'Lloyd', 'Grant', sep = ' ')
```

Vectorized:
```{r}
x <- c('Sheridan Grant', 'General Kenobi')
str_c('Hello there, ', x, '!')[2]  # I know I butchered the actual quote don't @ me
str_c(x, rev(x), 1:4)
```

Collapsing:
```{r}
str_c(rep(x, 2), collapse = ' admires ')  # a classic bromance
```

Trimming:
```{r}
str_trim('   Have you heard the story?   ', side = 'left')
str_trim('   Have you heard the story?   ', side = 'right')
str_trim('   Have you heard the story?   ', side = 'both')
str_squish('   Have    you       heard      the      story?   ')
```

Subsetting:
```{r}
str_sub(x, 3)
str_sub(x, -3)
str_sub(x, 3, 12)
str_sub(x, 3, -3)
```

Chat Q1: can I always rewrite str_sub(x, a, b) as str_sub(x, a, -c)?
```{r}
y <- c('hi', 'hey')
str_sub(y, 1, 2)
str_sub(y, 1, -2)
```

### Regular Expressions

You may have seen '\n' in my solutions, particularly when I use cat:
```{r}
cat('Name is:', readline('Name? '), '\n',
    'Fav number is:', readline('Fav number? '))
```

This is interpreted as a newline, even though I didn't type a newline! '\n' is a regular expression, or regex.

Basic pattern matching:
```{r}
x <- c(x, 'Hello there.', 'What about the droid attack on the wookies?')
str_view(x, 'er')
str_view_all(x, '. .')  #'.' is a regex for "any single character"
str_view(x, '\.')  # This doesn't work because backlash is itself a character
str_view(x, '\\.')  # 'Double escape'
str_view(x, '^G')  # ^ anchors to beginning
str_view(x, 't$')  # $ anchors to end
```

How to actually use it in code?
```{r}
str_detect(x, 'er')
str_detect(x, '\\.')
```

Email Q1: email me a line of code that determines if a string x begins with x, y, or z.

### Country Search

Identifying countries
```{r}
covid$Country_Region %>% unique() -> country
country %>% str_detect('Republic') %>% sum()
country %>% str_subset('Republic')
country %>% str_extract('.*. .*')
country %>% str_subset('z')
country %>% str_subset('(?i)[z]')  # I just Googled "case insensitive"
country %>% str_subset("\\([^()]+\\)")  # Oops--Republic of the Congo vs. DRC
country %>% str_subset('e{2,}|o{2,}')  # Runs of at least 2 letters
```

### Quora Troll Identification

Help Quora flag troll questions. (Machine learning aside.)
Email Q2: email me another real-world example in which humans "labeling" a binary outcome may be mistaken or biased.
```{r}
mean(fastQuora$target)
```

6% troll questions. Are questions about vaccines more likely to be trolling?

```{r}
mean(fastQuora[str_detect(question_text, '(?i)vaccin'),'target'][[1]])
```

OH yes. How 'bout ones that include the word "autism" or "autistic" as well?

```{r}
fastQuora[str_detect(question_text, '(?i)vaccine.*autis|autis.*vaccine'),]$target %>% mean()
```

Aha! How'd this work? '.' stands for any character, '*' for "0 or more repetitions" so ".*" for as many characters between the two words as we want!

Chat Q2: what's an easier way to check for the presence of both these words? One that doesn't require you to know '.' or '*'?

Email Q3: find a regex that checks if an email address is valid, and email it to me. It's okay if it takes more than 1 line in the email.

Chat Q2 answer:
```{r}
fastQuora %>% 
  filter(str_detect(question_text, '(?i)vaccine'),
                     str_detect(question_text, '(?i)autis')) %>%
  summarize(percentTroll = mean(target))
```

Chat Q3: let's find all the questions with more than one question mark in a row. Submit a regex in the chat, I'll test some of 'em without saying who sent it.

```{r}
fastQuora[str_detect(question_text, '\\?{2,}'),]$target %>% mean()
```

Breakout: how many of these questions mention at least one US state? Hints: R has a built-in list of states, str_detect is vectorized in both arguments.