\documentclass[12pt]{article}

\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
\graphicspath{{../charts/}}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[shortlabels]{enumitem}
\usepackage{color}
\usepackage{listings}
\lstset{breaklines=true}
\usepackage{appendix}
\usepackage[colorlinks]{hyperref}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{multicol}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

\newcommand{\Prob}{\text{P}}
\newcommand{\E}{\text{E}}
\newcommand{\Var}{\text{Var}}
\newcommand{\Cov}{\text{Cov}}
\newcommand{\sd}{\text{sd}}
\newcommand{\KL}{\text{KL}}
\newcommand{\I}{\text{I}}

\newcommand{\Norm}{\text{N}}
\newcommand{\Unif}{\text{U}}
\newcommand{\Pois}{\text{Pois}}
\newcommand{\Cauchy}{\text{Cauchy}}
\newcommand{\Laplace}{\text{LaPlace}}
\newcommand{\Binom}{\text{Binom}}

\newcommand{\Ind}{\textbf{1}}
\newcommand{\sign}{\text{sign}}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}
\newcommand{\iid}{\overset{\text{i.i.d.}}{\sim}}

\newcommand{\Rr}{\mathbb{R}}
\newcommand{\Ff}{\mathbb{F}}
\newcommand{\Pp}{\mathbb{P}}
\newcommand{\Qq}{\mathbb{Q}}

\newcommand{\logit}{\text{logit}}
\newcommand{\expit}{\text{expit}}

\newcommand{\Ascript}{\mathcal{A}}
\newcommand{\Gscript}{\mathcal{G}}
\newcommand{\Rscript}{\mathcal{R}}
\newcommand{\Hscript}{\mathcal{H}}
\newcommand{\Xscript}{\mathcal{X}}
\newcommand{\Yscript}{\mathcal{Y}}
\newcommand{\Oscript}{\mathcal{O}}
\newcommand{\Pscript}{\mathcal{P}}
\newcommand{\Mscript}{\mathcal{M}}

\title{STAT 302 Final Project Verbal Assessment Schedule (First Draft)}
\author{Sheridan Grant}
\date{Thursday, June 11}

\begin{document}\sloppy

\maketitle

If the time listed does not work for you (or your partner, if you have one), email me and request a time between 8:30 and midnight Pacific time on Thursday (apologies if I forgot your time zone). I have only scheduled people who I remember are living in a distant time zone or who have asked me to in the 8pm-midnight range---I expect there will be more who want to be scheduled at night, which is okay. If you need a different time, give me the earliest time you are available. If \textit{none} of these times work for you, please tell me as many times you are available on the 10th or 11th as possible. If you are not listed and have not arranged something with me already, please email me and let me know ASAP.

\textbf{If you do not email me, I will assume the time scheduled works for you. You alone are responsible for getting the time zone right---all times listed here are Pacific (Seattle) time on June 11.}

I will enable the Zoom waiting room; \textbf{show up ready to present 15 minutes before your scheduled time}, unless you are presenting exactly at 2:30pm or 8pm, in which case you can arrive just 2 minutes early. Assessments will be 5-6 min for individuals and 8-10 min for partners and some time slots will be empty, so these times are not exact.

\begin{multicols}{2}

\textbf{Afternoon sessions:}

2:30-40: Lukas \& Suh Young 

2:40-45: Samuel 

2:45-55: Yiyang \& Zejun 

2:55-3:00: Munan 

3:00-05: Alyssa 

3:05-10: Helen 

3:10-15: Zhuoran 

3:15-25: Aiden \& Yujia 

3:25-30: Cooper 

3:30-35: Shay 

3:35-40: Coco 

3:40-50: Winnie \& Yuchen 

3:55-4:00: Kyle

4:05-15: Lingya \& Carole 

4:15-20: Anas

\textbf{Evening sessions:}

8:00-10: Chris \& Tim 

8:10-15: Mark \& Chandrashree 

8:15-20: Jungki 

8:20-25: Megan

8:25-30: Tiffany

\end{multicols}

\end{document}